Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-04-11 main.tex
:pencil: Update discussions

		Problem~\eqref{op:original} is intricate with coupled variables in non-convex expressions \eqref{ob:original}, \eqref{co:original_rate}, \eqref{co:original_modulus}. To obtain a feasible solution, we propose an BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and the splitting ratio, until convergence.
		% \begin{remark}\label{re:irs_subchannel_alignment}
		% 	As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem. Following Remark~\ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflecting element can simultaneously align the corresponding AP-IRS-UE channel with the AP-UE channel at all subbands. In this case, the strengths of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
		% \end{remark}

@@

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a horizontal line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links. Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}. All channels are assumed NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is set to \SI{2}{\dBi}. For the algorithms, the number of candidates for Gaussian randomization is $Q=10^{3}$, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity. All R-E regions are averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

		\begin{table*}[!t]
			\caption{The maximum value of $1-\nu$ over all R-E samples during BCD and LC-BCD algorithms for all tested channel realizations}
			\label{ta:eigen_ratio}
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
			\hline
			\multicolumn{2}{|c|}{\multirow{2}{*}{}} & \multicolumn{3}{c|}{$M$} & \multicolumn{3}{c|}{$N$} & \multicolumn{3}{c|}{$L$} & \multicolumn{2}{c|}{$B$} \\ \cline{3-13}
			\multicolumn{2}{|c|}{} & \num{1} & \num{2} & \num{4} & \num{1} & \num{4} & \num{16} & \num{20} & \num{40} & \num{80} & \SI{1}{\MHz} & \SI{10}{\MHz} \\ \hline
			$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
			$[\times \num{e-16}]$ & LC & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
			\end{tabular}
		\end{table*}

		We first provide numerical proof on the strict convergence (thus local optimality) of both BCD algorithms. Too see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$. Since $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$. Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over all R-E samples during both BCD algorithms. With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations. It suggests that the rank constraint \ref{co:irs_rank} can be relaxed without performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~\ref{pr:bcd} always hold such that both BCD algorithms converge to local optimal.

@@

		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \textit{First,} it is observed that increasing $N$ reduces the per-subband rate $R/N$ but boosts the harvested energy. It is because each subband receives less power but more balanced DC terms are introduced to boost the harvested energy. On the other hand, Fig.~\ref{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order. It demonstrated that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. This observation origins from the rectifier nonlinearity. Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order DC terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2} while the multisine has $(2N^3+N)/3$ monomials. Hence, the benefit of multisine outstands for a sufficiently large $N$. \textit{Second,} the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e. a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}). Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving mode, both heavily depends on the number of subbands.

@@

		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$. A \textit{first} observation is that, different from the active Amplify-and-Forward (AF) relay with the optimal development location around the midpoint \cite{Li2017}, placing the IRS closer to either the transmitter or the receiver would further improve the R-E tradeoff. It origins from the product-distance path loss model that applies to finite-size element reflection. As shown in Fig.~\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large distance (greater than \SI{10}{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup, since signal attenuation increases fast at a short distance and experiences marginal effect at a long distance. On the other hand, it also suggests that developing an IRS next to the AP can effectively extend the operation range of SWIPT systems. Considering the passive characteristic of the IRS, opportunities are that it can be directly supported by the SWIPT network. A \textit{second} observation from Fig.~\ref{fi:path_loss} is that there exist two optimal IRS development locations that minimize the path loss production $\Lambda_{\mathrm{I}}\Lambda_R$. It implies that two IRSs may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the UE.

@@

		The impacts of the number of transmit antennas $M$ and IRS elements $L$ on the R-E behavior are revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}. \textit{First,} adding either active or passive elements enhances the equivalent channel strength to boost information and power transfer. Interestingly, it has negligible influence on the optimal transceiving strategy because both rate and current are amplified that preserves the general trend of the R-E boundary. \textit{Second,} the passive beamforming has a larger array gain and power scaling order than the active beamforming. This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT, where the Adaptive Single Sinewave (ASS) allocates all power to the sine wave on the strongest subband and is optimal for the linear harvester model \cite{Clerckx2016a}. For the MRT active precoder, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR that corresponds to a transmit array gain of $M$ and a doubled harvester input power. Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase that validates the active scaling law in the order of $M^2$ \cite{Clerckx2016a}. On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB} that implies a reflect array gain of $L^2$. An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$. Hence, doubling IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), corresponding to a passive scaling law in the order of $L^4$. Compared with active antennas, the IRS achieves higher array gain and power scaling order by passive elements with frequency-dependent reflection, but a very large $L$ is required to compensate the double fading of the auxiliary link. Moreover, the ASS strategy exploit no harvester nonlinearity and ends up with a nearly \SI{20}{\dB} gap with SMF and GP. These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting the harvester nonlinearity in the passive beamforming design.

@@

		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT. The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies. The adaptive IRS adjusts the passive beamforming for different rate constraints by Algorithm~\ref{al:sca}. The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:lc} then fixed for the whole R-E region (i.e. the boundary is obtained by varying the waveform amplitude and splitting ratio). \textit{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited. Their achievable R-E regions coincide because the antenna mode reflection of the random IRS is cancelled out after averaging over channel realizations. \textit{Second,} the performance of non-random IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large. In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes unobvious and the auxiliary channels can be roughly maximized at all subbands. It suggests that for narrowband SWIPT, the optimal passive beamforming of any R-E point is roughly optimal for the whole R-E region, which can be approximated in the closed form (by aligning the auxiliary channel with the direct channel) when a single transmit antenna is used at the AP. On the other hand, the optimal reflection coefficient varies at different R-E points for broadband SWIPT, since the information and power transfer prefer different channel strength distribution in the frequency domain. By adaptive passive beamforming, the channel strength can be either amplified at few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power.

		% The rate-dependent adaptive IRS strategy adjusts the passive beamforming for each point on the R-E boundary, while the WIT/WPT-based non-adaptive IRS schemes only optimize the phase shifts for information and power purposes (correspond to the points on the $x$ and $y$ axes, respectively). To gain some insight into the IRS behavior, we compare the results above to no IRS and an ideal Frequency-Selective (FS) IRS.

		% \textit{First,} it is observed that the assistance of the IRS effectively enlarges the achievable R-E region for both narrowband and broadband transmissions.
		% performance of all four IRS strategies coincide with each other for narrowband SWIPT. It suggests that the optimal passive beamforming obtained for any R-E point is also optimal for the whole R-E region. Therefore, for a given channel, we can fix the active and passive beamforming, and only adapt the waveform and splitting ratio to achieve different R-E performance. This is because when the bandwidth is small, all channels are approximately flat such that the optimal ideal reflection coefficients at all subbands are approximately the same. Also, the subchannel tradeoff in Remark~\ref{re:irs_frequency_flat} does not exist as the auxiliary channel can be simultaneously maximized at different frequencies. \textit{Third,} a joint optimization of waveform, active and passive beamforming, and splitting ratio is necessary to maximize the R-E tradeoff for broadband SWIPT. Recall Remark~\ref{re:irs_subchannel_alignment} that WIT and WPT prefer different subchannel strength distribution. By adaptive passive beamforming, the channel strength can either be concentrated in few strongest subbands to enhance the rate at a low SNR, or be spread evenly over all subbands to boost the output DC power. The advantage of such a smart channel control is prominent for broadband SWIPT where the strength can vary significantly for different subbands.

		\begin{subsection}{Imperfect CSIT}
			Due to the general lack of RF-chains at the IRS, accurate CSIT acquisition can be challenging especially for a short coherence time. Hence, we consider an imperfect CSIT model and denote the estimation of the cascaded links at subband $n$ as
			\begin{equation}
				\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
			\end{equation}
			where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries in i.i.d. CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$. Perfect CSIT can be regarded as a special case with $\epsilon_{n} = 0$. % For each direct and cascaded channel, we provide \num{100} channel estimates and examine the average R-E behavior.
		\end{subsection}

		\begin{subsection}{Quantized IRS}
			Recall in Remark \ref{re:reflection_coefficient} that one needs to vary the element impedance to adjust the reflection coefficient. To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to quantize each reflection coefficient by $b$ bits.

			\begin{figure}[!t]
				\centering
				\subfloat[Quantized IRS\label{fi:re_quantization}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/re_quantization.tex}
					}
				}
				\subfloat[Imperfect CSIT\label{fi:re_csi}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/re_csi.tex}
					}
				}
				\caption{Average R-E region with quantized IRS and imperfect cascaded CSIT for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
			\end{figure}
		\end{subsection}
	\end{section}

	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
		This paper proposes a novel IRS-aided multi-carrier downlink MISO SWIPT system to enhance the rate and energy tradeoff of a single user. We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the splitting ratio at the receiver to enlarge the achievable R-E region. Different from the existing IRS-aided SWIPT literature, this paper leverages rectifier nonlinearity in passive beamforming design and investigates a multi-carrier transmission for practical co-localized receiver architectures. Efficient algorithms based on the BCD, SCA, SDR and GP techniques are numerically demonstrated feasible for all tested channel realizations under different configurations. We confirm that considering harvester nonlinearity, a dedicated power waveform is generally required to boost the R-E tradeoff. When developed near the transmitter, the IRS can provide effective channel enhancement to enlarge the R-E region and expand the operation range. Compared with the transmit antenna, the IRS element has no design flexibility in the frequency domain, but it integrates the coherent combining and transmission techniques in a fully passive manner to further boost the array gain and power scaling effects. Finally, the optimal passive beamforming at any R-E point is also optimal for the whole R-E region of narrowband transmission, and the rate-dependent adaptive passive beamforming is beneficial for broadband transmission.

>>>>

		Problem~\eqref{op:original} is intricate with coupled variables in non-convex expressions \eqref{ob:original}, \eqref{co:original_rate}, \eqref{co:original_modulus}. To obtain a feasible solution, we propose an BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and the splitting ratio, until convergence.

@@

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a horizontal line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links. Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}. Denote $\Lambda_{\mathrm{D}},\Lambda_{\mathrm{I}},\Lambda_{\mathrm{R}}$ as the path loss of direct, incident and reflective links. All channels are assumed NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is set to \SI{2}{\dBi}. For the algorithms, the number of candidates for Gaussian randomization is $Q=10^{3}$, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity. Each R-E region is averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

		\begin{table*}[!t]
			\caption{The maximum value of $1-\nu$ over all R-E samples during BCD and LC-BCD algorithms for all tested channel realizations}
			\label{ta:eigen_ratio}
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
			\hline
			\multicolumn{2}{|c|}{\multirow{2}{*}{}} & \multicolumn{3}{c|}{$M$} & \multicolumn{3}{c|}{$N$} & \multicolumn{3}{c|}{$L$} & \multicolumn{2}{c|}{$B$} \\ \cline{3-13}
			\multicolumn{2}{|c|}{} & \num{1} & \num{2} & \num{4} & \num{1} & \num{4} & \num{16} & \num{20} & \num{40} & \num{80} & \SI{1}{\MHz} & \SI{10}{\MHz} \\ \hline
			$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
			$[\times \num{e-16}]$ & LC & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
			\end{tabular}
		\end{table*}

		We first provide numerical proof on the strict convergence (thus local optimality) of both BCD algorithms. Too see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$. Since $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$. Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over all R-E samples during both BCD algorithms. With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations. It suggests that the rank constraint \ref{co:irs_rank} can be relaxed with negligible performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~\ref{pr:bcd} always hold such that both BCD algorithms converge to local optimal.

@@

		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \textit{First,} it is observed that increasing $N$ reduces the per-subband rate $R/N$ but boosts the harvested energy. It is because less power is given to each subband but more balanced DC terms are introduced to boost the harvested energy. On the other hand, Fig.~\ref{fi:waveform_subband} sorts the modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT in descending order. It demonstrated that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. This observation origins from the rectifier nonlinearity. Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2} while the multisine has $(2N^3+N)/3$ monomials. Hence, the benefit of multisine outstands for a sufficiently large $N$. \textit{Second,} the R-E region is convex for $N=2,4$ and concave-convex for $N=8,16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e. a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}). Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving mode, both heavily depends on the number of subbands.

@@

		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$. Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020}. Moreover, there exist two optimal IRS coordinates with $d_{\mathrm{H}}=0.6$ and \SI{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the R-E tradeoff. It suggests that equipping the AP with an IRS can potentially extend the operation range of SWIPT systems. Considering the passive characteristic of the IRS, chances are that it can be directly supported by the SWIPT network.

@@

		The impacts of the number of transmit antennas $M$ and IRS elements $L$ on the R-E behavior are revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}. \textit{First,} adding either active or passive elements enhances the equivalent channel strength to boost information and power transfer. Interestingly, it has negligible influence on the optimal transceiving strategy because both rate and current are amplified that preserves the general trend of the R-E boundary. \textit{Second,} passive beamforming has a larger array gain and power scaling order than active beamforming. This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} for the case of WIT and WPT, where the Adaptive Single Sinewave (ASS) allocates all power to the sine wave on the strongest subband and is optimal for WPT with linear harvester model \cite{Clerckx2016a}. For active beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the output SNR that corresponds to a transmit array gain of $M$ and a doubled harvester input power. Thanks to the rectenna nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase that validates the active scaling law in the order of $M^2$ \cite{Clerckx2016a}. On the other hand, when the IRS is very close to the AP, doubling $L$ increases the output SNR up to \SI{6}{\dB} that implies a reflect array gain of $L^2$. An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$. Hence, doubling IRS elements brings a four-fold increase on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), corresponding to a passive scaling law in the order of $L^4$. Compared with active antennas, the IRS achieves higher array gain and power scaling order using passive elements with frequency-dependent reflection, but a very large $L$ is required to compensate the double fading of the auxiliary link. Moreover, the ASS strategy exploit no harvester nonlinearity and ends up with a nearly \SI{20}{\dB} current gap with SMF and GP. These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting the harvester nonlinearity in the passive beamforming design.

@@

		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT. The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies. The adaptive IRS adjusts the passive beamforming for different rate constraints by Algorithm~\ref{al:sca}. The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:lc} then fixed for the whole R-E region (i.e. the boundary is obtained by varying the waveform amplitude and splitting ratio). \textit{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited. Their achievable R-E regions coincide because the antenna mode reflection of the random IRS is cancelled out after averaging over channel realizations. \textit{Second,} the performance of non-random IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large. In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant and the auxiliary channels can be roughly maximized at all subbands. It suggests that for narrowband SWIPT, the optimal passive beamforming of any R-E point is roughly optimal for the whole R-E region, which can be approximated in the closed form (by aligning the auxiliary channel with the direct channel) when a single transmit antenna is used at the AP. On the other hand, the optimal reflection coefficient varies at different R-E points for broadband SWIPT, since the information and power transfer prefer different channel strength distribution in the frequency domain. By adaptive passive beamforming, the channel strength can be either amplified at few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power. It shows the R-E advantage of adaptive passive beamforming via Algorithm~\ref{al:sca} for broadband SWIPT.

		\begin{figure}[!t]
			\centering
			\subfloat[Imperfect CSIT\label{fi:re_csi}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_csi.tex}
				}
			}
			\subfloat[Quantized IRS\label{fi:re_quantization}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_quantization.tex}
				}
			}
			\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

		We then explore the impact of imperfect cascaded CSIT and quantized IRS on the R-E performance. Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis. Consider an imperfect CSIT model where the estimation of the cascaded link at subband $n$ is
		\begin{equation}
			\hat{\boldsymbol{V}}_{n} = \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
		\end{equation}
		where $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d. CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$. Perfect CSIT can be regarded as a special case with $\epsilon_{n}=0$. Note that the estimation at different subbands are independent but the subchannel responses are correlated. Figure~\ref{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for different $L$.

		Since the available reflection coefficient depends on the element impedance set, we quantize each reflection coefficient by $b$ bits and design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ to reduce the circuit complexity and control overhead. Figure~\ref{fi:re_quantization} suggests that even $b=1$ (i.e. two-state reflection) brings considerable R-E gain over the benchmark scheme, and the performance gap between $b=4$ and unquantized IRS is negligible.
	\end{section}

	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
		This paper proposes a novel IRS-aided multi-carrier MISO SWIPT system to enhance the rate and energy tradeoff of a single user. We perform a joint optimization of the waveform and active beamforming at the transmitter, the passive beamforming at the IRS, and the splitting ratio at the receiver to enlarge the achievable R-E region. Different from the existing IRS-aided SWIPT literature, this paper leverages rectifier nonlinearity in passive beamforming design and investigates a multi-carrier transmission for practical co-localized receiver architectures. Efficient algorithms based on the BCD, SCA, SDR and GP techniques are numerically demonstrated feasible for all tested channel realizations under different configurations. We confirm that considering harvester nonlinearity, a dedicated power waveform is generally required to boost the R-E tradeoff. When developed near the transmitter, the IRS can provide effective channel enhancement to enlarge the R-E region and expand the operation range. Compared with the transmit antenna, the IRS element has no design flexibility in the frequency domain, but it integrates the coherent combining and transmission techniques in a fully passive manner to further boost the array gain and power scaling effects. Finally, the optimal passive beamforming at any R-E point is also optimal for the whole R-E region of narrowband transmission, and the rate-dependent adaptive passive beamforming is beneficial for broadband transmission.
